### 2016-08-25 introduction.tex
New introduction

The upcoming 5G technology is targeting the controlling and steering of the Internet of Things (IoT) in real-time on global scale. This will break new ground for new markets such as driverless vehicles, manufacturing, humanoid robots, smart grids, and many more. With 5G, the number of wireless devices will increase by five times up to 50 billion devices \cite{cisco2011forecast}. It is generally believed, that those devices will not be connected in the same manner as current devices are connected today. Centralized system will collapse in terms of capacity, while distributed systems appear as an alternative. Therefore the communication architecture in future systems will be dominated by mesh technologies. Mesh technology has been known for sensor and ad hoc networks or mobile cloud scenarios, but the technical requirements on 5G mesh-based communication systems are dramatically increasing. Future mesh networks need to support high data rate, low latency, security, network availability and heterogeneous devices. In state of the art systems those requirements are traded-off with each other, but in the 5G context we cannot do this anymore.

@@

The emergence of powerful and inexpensive single-board computers running full versions of a standard \ac{OS} from many possible opens new possibilities in this area. This not only allows to seamlessly develop implementations that are compatible with higher end devices but also allows the reuse stable software from widely-used \ac{OS}. For example, the work in \cite{cox2014iridis} provides a detailed description of a \ac{Raspi}~\cite{making_of_pi} testbed ideal for educational applications. Here the authors also include computational, throughput and storage benchmarks to assess its performance. However, this work indicates provides only a basic description of how to set up the required software and also mentions that its maintenance could be time-demading. Moreover, this work does not consider possible network coding applications. Given this set of specific needs, in this work we present the design, key step-by-step instructions and mechanisms to setup, configurate and maintain of an inexpensive testbed using \ac{Raspi} devices for networking (wireless or wired) and storage applications including \ac{RLNC} functionalities into the testbed through Kodo. Nevertheless, the architecture itself is not bounded to the networking area and can be used for other applications that require replicable results with \ac{Raspi}~\cite{leccese2014smartcity,leccese2014newimaging,sapes2016finger}\textcolor{red}{move citations or rewrite a bit here}. Our work for the testbed procedure is organized as follows: Section~\ref{sec:overview} introduces the testbed system. In Section~\ref{sec:image_setup}, we provide details about the testbed setup, scripts, configuration files and connectivity. In Section~\ref{sec:overlay_fs}, we elaborate on the need and setup for an overlay filesystem for our testbed in order to have both persistent and non-persistent data on it as an optional step. Section~\ref{sec:tools} describes a set of automation and monitoring tools that can be included in the testbed to simplify the execution of routinary and repetitive tasks. Section~\ref{sec:cross_compilation} elaborates on the compilation of the Kodo library for the \ac{Raspi}. Conclusions and future work are reviewed in Section~\ref{sec:conclusions}. Finally, a set of alternative commands, in case the ones presented in this work might not be executed, are discussed in the Appendices.

>>>>

The upcoming 5G technology is targeting the controlling and steering of the \ac{IoT} in real-time on global scale. This will break new ground for new markets such as driverless vehicles, manufacturing, humanoid robots, smart grids, and many more. With 5G, the number of wireless devices will increase by five times up to 50 billion devices \cite{cisco2011forecast}. It is generally believed, that those devices will not be connected in the same manner as current devices are connected today. Centralized system will collapse in terms of capacity, while distributed systems appear as an alternative. Therefore the communication architecture in future systems will be dominated by mesh technologies. Mesh technology has been known for sensor and ad hoc networks or mobile cloud scenarios, but the technical requirements on 5G mesh-based communication systems are dramatically increasing. Future mesh networks need to support high data rate, low latency, security, network availability and heterogeneous devices to ensure high \ac{QoE} for the final user. In state of the art systems those requirements are traded-off with each other, but in the 5G context we cannot do this anymore.

@@

The emergence of powerful and inexpensive single-board computers running full versions of a standard \ac{OS} from many possible opens new possibilities in this area. This not only allows to seamlessly develop implementations that are compatible with higher end devices but also allows the reuse stable software from widely-used \ac{OS}. For example, the work in \cite{cox2014iridis} provides a detailed description of a \ac{Raspi}~\cite{making_of_pi} testbed ideal for educational applications. Here the authors also include computational, throughput and storage benchmarks to assess its performance. However, this work indicates only a basic description of how to set up the required software and also mentions that its maintenance could be time-demading. Moreover, this work does not consider possible network coding applications. Different studies of \ac{IoT} applications consider using the \ac{Raspi} for data processing: In \cite{leccese2014smartcity}, the \ac{Raspi} is the processing unit that coordinates and controls the activity of a public road isle of lamps and reports it to a monitoring center. A use case regarding remote environment surveillance is presented in \cite{leccese2014newimaging}, where the \ac{Raspi} reports air pressure, humidity and temperature of the locations of cultural paintings plus high-resolution images of the paintings themselves. This data is sent to a monitoring center to ensure the preservation of the paintings. Further, authors in \cite{sapes2016finger} utilize the \ac{Raspi} to act as the data server in a finger scanning application that collects the fingerprints. Even though all these applications consider the use of the \ac{Raspi} as a core block, they provide few to no description of their procedures to configure the \ac{Raspi} making their discussed results difficult to reproduce. Moreover, these applications become cumbersome to maintain as their considered systems could potentially scale when aiming to serve more users. Furthermore, the current way that the data is sent in the considered networks for these \ac{IoT} applications will not be feasible in future 5G systems as mentioned previously.

Given this set of specific needs, in this work we present the design, key step-by-step instructions and mechanisms to setup, configurate and maintain of an inexpensive testbed using potentially several \ac{Raspi} devices for networking (wireless or wired) and storage applications including \ac{RLNC} functionalities into the testbed through Kodo. Nevertheless, the architecture itself is not bounded to the networking area and can be used for other applications that require replicable results with the \ac{Raspi}. Our work for the testbed procedure is organized as follows: Section~\ref{sec:overview} introduces the testbed system. In Section~\ref{sec:image_setup}, we provide details about the testbed setup, scripts, configuration files and connectivity. In Section~\ref{sec:overlay_fs}, we elaborate on the need and setup for an overlay filesystem for our testbed in order to have both persistent and non-persistent data on it as an optional step. Section~\ref{sec:tools} describes a set of automation and monitoring tools that can be included in the testbed to simplify the execution of routinary and repetitive tasks. Section~\ref{sec:cross_compilation} elaborates on the compilation of the Kodo library for the \ac{Raspi}. Conclusions and future work are reviewed in Section~\ref{sec:conclusions}. Finally, a set of alternative commands, in case the ones presented in this work might not be executed, are discussed in the Appendices.
